---
title: "Case Study Assessment"
output: github_document
date: 10-10-2023
---

Class Package Library Import
```{r}
library(p8105.datasets)
library(tidyverse)
library(ggridges)


#Global Markdown Knitting Settings
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

nyc_airbnb = nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location/2)
```

# Brainstorm Questions
- Where are AirBNBs expensive?
- Borough? Neighborhood?
- Do other factors (room type affect price?) What about rating?
- How long are AirBNBs active?
- Are Air BNBs Illegal and do they shut down?
- Which units have the most availability?
- How is the review socore impacted by location?
- How many apartments are run by one host?


## First Questions - Where are AirBNBs Expensive? How does rating impact price? 
First try by myself
```{r}
summary(nyc_airbnb)

nyc_airbnb |> 
  ggplot(aes(x = stars, y = price, fill = borough)) + 
  geom_violin()
  
```

Guided coding 

```{r}
nyc_airbnb |> 
  count(borough)

```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

ˆ
```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt", borough == "Manhattan") |>
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(), 
    mean_price = mean(price)) |> 
  arrange(desc(mean_price))
  
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt", borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot()

```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt", borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```


# Starting to use location data
```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt", borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```


```{r}
library(leaflet)

#Basic Leaflet
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addTiles() |> 
  addMarkers(~lat, ~long)
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = .5)
```

